---
title: "Software Architecture Quality report on Architectural Smells in <Project-Name>"
output: html_notebook
---

```{r message=FALSE, warning=FALSE, include=FALSE}
source("report-plotting.R")
df.smells <- read.csv("/home/fenn/git/data/trackASOutput/tics/smell-characteristics-consecOnly.csv")
df.sizes <- read.csv("/home/fenn/git/data/trackASOutput/tics/project-sizes-consecOnly.csv")
df <- cleanData(df.smells, df.sizes)
df.smells <- df$df.smells
df.sizes <- df$df.sizes
```

# Introduction
Explain what this report is meant for and introduce to AS (perhaps link to an explanation)

# Generic report
Some numbers and plots that report generic values (e.g n. of smells over time by type, n. of smells in last version by type)

```{r}
plotNumOfSmellsOverTimeByType(df.smells)
```

```{r}
plotNumOfSmellsLastVersionByType(df.smells)
```

```{r}
plotComponentCountPerVersion(df.sizes)
```

## System evolution


# Specific report
e.g. Component affected by most smell, oldest smell (interest paid)

# Suggested Refactoring Actions
Which smells/components to refactor first, why,



